Probabilities of polar aligned disks in binary star systems

### 2024-04-17 src/tex/ms.tex
Rearrange definitions of orbital parameters

\subsubsection{Determining the state}
\label{subsubsec:state}
We integrate the system 5 (third-body) orbits at a time, capturing the positions and velocities of each particle afterwards. \RGM{I'm not sure what the 5 means?}
%Between each step we attempt to assign an end-state to the system.
\RGM{We describe the type of orbit by}
%This is done by 
computing $i$ and $\Omega$ \RGM{include equations and descriptions for i and $\Omega$ here} and checking them against
two criteria:
\begin{enumerate}
    \item Has $\Delta\Omega$ changed sign? In a precessing orbit $\Omega$ changes monotonically. If 
    $\frac{d\Omega}{dt}$ changes from positive to negative (or vise-versa) then we can be sure we have found a librating state.
    \label{item:omega}
    \item Has $i~\sin{\Omega}$ crossed zero? In a librating state this quantity will never change sign. 
    \label{item:sign}
\end{enumerate}
 Determining the state is done iteratively and only requires that $i$ and $\Omega$
be known at each timestep. If neither criteria are true then we do not yet have enough information, and we continue the integration.
If criterion \ref{item:omega} is true then the system is librating. If criterion \ref{item:sign} is true then the system is precessing.
There is no configuration that would allow both criteria to be true.

In order to compute $i$ and $\Omega$ we must first define a coordinate system. {\sc rebound} outputs the positions and
velocities of each particle in the center-of-mass frame. We then use the binary to define a time-dependent coordinate system.
We define the $z$-axis to be along the angular momentum vector of the binary, the $x$-axis to be along the eccentricity vector, and the
$y$-axis so that the coordinate system is right-handed.

\begin{equation}
\begin{aligned}
    \hat{\bm{z}} & = \bm{L}/\|\bm{L}\| \\
    \hat{\bm{x}} & = \bm{e}/\|\bm{e}\| \\
    \hat{\bm{y}} & = - \hat{\bm{x}} \times \hat{\bm{z}}
    \label{eq:coords}
\end{aligned}
\end{equation}
We can then compute $i$ and $\Omega$ from the angular momentum $\bm{L}$.

\begin{equation}
    \cos{i} = \frac{\bm{L} \cdot \hat{z}}{\|\bm{L}\|}
    \label{eq:inclination}
\end{equation}

@@

>>>>

\subsubsection{Determining the state}
\label{subsubsec:state}
We integrate the system, checking its state every 5 orbits of the third body.
We describe the type of orbit by computing the mutual inclination $i$ and the
longitude of the ascending node $\Omega$, which are defined:

\begin{equation}
    \cos{i} = \frac{\bm{L} \cdot \hat{\bm{z}}}{\|\bm{L}\|}
    \label{eq:inclination}
\end{equation}

and

@@

Where $\bm{L}$ is the angular momentum of the third body.
The coordinate system is defined relative to the binary, with the $z$-axis to be along the
angular momentum vector, the $x$-axis to be along the eccentricity vector, and the
$y$-axis so that the coordinate system is right-handed.

\begin{equation}
    \begin{aligned}
        \hat{\bm{z}} & = \bm{L}/\|\bm{L}\| \\
        \hat{\bm{x}} & = \bm{e}/\|\bm{e}\| \\
        \hat{\bm{y}} & = - \hat{\bm{x}} \times \hat{\bm{z}}
        \label{eq:coords}
    \end{aligned}
\end{equation}

The final state of the three-body system is assessed according to two criteria:

\begin{enumerate}
    \item Has $\Delta\Omega$ changed sign? In a precessing orbit $\Omega$ changes monotonically. If 
    $\frac{d\Omega}{dt}$ changes from positive to negative (or vise-versa) then we can be sure we have found a librating state.
    \label{item:omega}
    \item Has $i~\sin{\Omega}$ crossed zero? In a librating state this quantity will never change sign. 
    \label{item:sign}
\end{enumerate}

If neither criteria are true then we do not yet have enough information, and we continue the integration.
If criterion \ref{item:omega} is true then the system is librating. If criterion \ref{item:sign} is true then the system is precessing.
There is no configuration that would allow both criteria to be true.
